Do I Need to Model You in order to Learn With You?

### 2015-04-01 mutual-modeling.tex
{A -> $A$}

Initial common grounds are also initiated by co-presence: they include events to
which A and B attended together~\citep{clark2002definite} in the physical space
or in our cultural space (\eg ‘09-11'). Co-presence means that we can refer to
a shared objects and event,-s it does of course not imply that we give them the
same meaning. Namely, a shared screen does not mean a shared
understanding~\citep{dillenbourg2006sharing}.

@@

Mutual modelling does not occur in a vacuum but it is highly contextualized. REF
reviews the features of the collaborative situation, namely the media
(cotemporality… ), may facilitate or hamper mutual modelling. Hutchins (SILENCE)
reported a study in which a short silence between two pilots was perfectly
interpreted because it occurred in a highly constrained communication context.
Some environments are more productive than others in helping peers to detect
their misunderstandings. Roschelle~\citep{roschelle1995construction} reformulate
the design of CSCL interfaces as providing ways for peer to detect and repairs
their misunderstanding. In CSCW, researchers have explored various so-called
``awareness tools'', \ie functionalities that inform A is about B's actions that A
could not directly perceived because B was working on a different subset of the
virtual space. Different awareness tools will be addressed in this contribution
since they allowed us to manipulate experimentally the mutual modelling activity.

@@

To report experiments on mutual modelling, we suggest
the notation \model{A}{B}{X} to denote ``A knows that B knows X''. This is a
simple but useful reduction to reason on mutual modelling. This
notation does not mean A has an explicit, monolithic representation of B: it
must be understood as an abstraction referring to complex socio-cognitive
processes. Besides, we refer to the \emph{degree of accuracy} of the model as
\Model{A}{B}{X}.

@@

Based on these 3 parameters, the probability of making an action $\alpha_{t_1}$ about
content X at time $t_1$ during task T in order to increase \Model{A}{B}{X}
at time $t_2$ is the ratio between how much it is needed  ((2)-(1)) and how much it
costs (3)~\citep{traum1996miscommunication}:

@@

    \begin{enumerate}
        \item \model{A}{B}{emotion}: how accurately A perceives B's emotional state
            (study 3);

        \item \model{A}{B}{actions} is about how well A guesses what action B has
            done (study 2) or will do next  (study 1)

        \item \model{A}{B}{knowledge}: how accurately A estimates B's knowledge
            with respect to the material they learn together (study 4 and 5)

@@

    \item $cost(\alpha)$ In all studies but study 4, the cost of  grounding is
        an independent variable. Study 3 uses media richness as independent
        variable, with the hypothesis that modelling emotions is ``cheaper'' with a
        richer medium, \ie  when peers can see each other.  Studies 1,2 and 4
        use awareness tools which, in principle, reduce the cost of mutual modelling, but do
        not eliminate all costs: if the tool provide A with information about
        what B does/knows, this additional information may actually increase
        cognitive load. Awareness tools constitute as a kind of mutual modelling prosthesis,
        and, like any prosthesis, they many augment mutual modelling (by facilitating it or
        even scaffolding it) or inhibit it (by making it useless).

@@

\begin{itemize}
    \item {\bf Capturing \model{A}{B}{X}}: The simplest method is to ask $A$ what (s)he
        believes about what $B$ knows, feels, intends to do, etc. This raises
        obvious methodological concerns since such a question triggers a
        modelling process beyond what it would 'naturally' be. To avoid this
        bias, one can estimate mutual modelling after task completion. Then, the
        obvious drawback are memory losses and by post-hoc reconstruction.  The
        first method was used in study 2 and the second one in the other
        studies. Another option would be to rely on external behavioural metrics
        like eye-tracking: we hypothesise for instance that the fixation time
        reflects the efforts engaged by the human to understand, hence, model,
        the others. Such an approach has however not yet been investigated in
        the presented studies.

@@

\begin{itemize}
    \item $\mathcal{H}_{1}$: $\mathcal{M}^{\circ}(A,B)$ depends upon A's ability or effort
        to model B,

    \item $\mathcal{H}_{2}$: $\mathcal{M}^{\circ}(A,B)$ depends upon  B's ability of
        effort to help A to model him/herself

    \item $\mathcal{H}_{3}$: $\mathcal{M}^{\circ}(A,B)$ depends upon the quality of
        interactions among A and B

@@

$\mathcal{H}_{2}$ is also called a second level modelling hypothesis since H
needs to monitor B to see if A understood him/her
$\mathcal{M}(B,(A,\mathcal{M}(A,B)))$

@@

This leads to two \emph{triangle questions} (Fig.~\ref{mm_triangles}): Do A and
B have the same accuracy when modelling C? $\Delta_2 = \Delta(\M{A}{C}{X},
\M{B}{C}{X})$. If it is the same, $\mathcal{H}_{2}$ and $\mathcal{H}_{3}$ gain
over $\mathcal{H}_{1}$

Conversely, does C model more accurately A than B? $\Delta_3= \Delta(\M{C}{A}{X},
\M{C}{B}{X})$ A positive answer would support $\mathcal{H}_{3}$.

@@

The independent variable was the availability of an awareness tool that shows to
player A  the location and gaze direction of player B. In the awareness
condition, players could switch to the \emph{scout mode} where they could view what
their partner was looking at. We hypothesize that this would enable subjects to
more accurately infer their teammate's intentions. Each player sat in front of a
distinct computer located in different rooms.

@@

In order to evaluate \gModel{A}{B} during the task, we used two questionnaires
(Fig.~\ref{study1:questionnaires}) that were displayed during each of the three
games, as a transparent layer appearing over the game display. The first
questionnaire concerned the player's intended actions. The second questionnaire
asked each player about what he thought her or his partner was intending to do.
Some answers were identical in both questionnaires (like ``adjusting a shot'')
while others were reversed (``to guide my partner'' versus ``to guide me''). We
chose this subjective measure of accuracy ($\Delta(\M{A}{B}{x}, \M{B}{B}{x})$)
rather than an objective measure (\ie the model \gmodel{A}{B} is compared to B's
next action) because some the activities proposed by the questionnaire were not
observable by the environment (\eg establishing a strategy). We counted
\Model{A}{B}{activity_{game_{i}}}) as the number of common answers between
questionnaires \gmodel{A}{B} and \gmodel{B}{B} in each game and computed the
average value a across the 3 games.

@@

This study concerns a collaborative game that occurred in the physical
space~\citep{nova2006underwhelming}. We studied whether players build an accurate
model of the path followed by their partners because this path reflected their
problem solving strategy. We used an objective measure of \gModel{A}{B}: the
distance between where A believes B has been walking and where B actually went.
The main hypothesis concerned the effect of awareness tools on group performance
and on \gModel{A}{B}.

@@

{\sc CatchBob} is a mobile game in which groups of 3 players have to solve a
joint task. The game was played on EPFL campus. Participants had to find a
virtual object (\emph{Bob}) and ``to catch it'' by forming a triangle around it.
Players used a Tablet PC that displayed a map of the campus and an indication of
their personal distance to Bob. Their annotations on the map were shared with
the two other players (A could see what B and C wrote). These annotations faded
out after a few minutes to avoid covering the full display. The awareness tool
displayed as well the location of the two other players on the map. The
availability of location awareness tool constituted our independent variable.

\begin{figure*}[h!t]
        \centering
        \begin{subfigure}{.3\textwidth}
            \includegraphics[width=\linewidth]{image6.png}
            \caption{A's drawing of B's path.}
        \end{subfigure}
        \begin{subfigure}{.3\textwidth}
            \includegraphics[width=\linewidth]{image7.png}
            \caption{Actual path followed by B.}
        \end{subfigure}
        \caption{Reported and actual path of one of the player, during the {\sc
        CatchBob} game.}
        \label{study2:paths}
\end{figure*}

@@

The independent variable was the awareness tool: the control condition (without
tool) and two experimental conditions: synchronous awareness (display current
position of each player) and asynchronous awareness (display current position of
each player and their recent spatial trace).  As a dependent variable, we had
the task performance which was the distance covered by the team to catch Bob and
\gModel{A}{B}. To estimate \gModel{A}{B}, we asked players to draw on paper
their own path and the path of each of their partners after the game. This
enabled us to calculate the number of errors players made while drawing the path
of their partners. We compared the path that player A attributed to B with B's
real path recorded by the system and the same for A \& C and B \& C as depicted
on Fig.~\ref{study2:paths}.

\gModel{A}{B} is the sum of errors made by A about B's paths. An error was
either drawing a place where the partner had not been or not drawing a place
where he/she had gone. One could argue that \gModel{A}{B} is biased by the
subjects' ability to translate their trajectories souvenir into a map drawing.
However, 85\% of subjects made no mistake at all when drawing their own path. We
therefore consider mistakes in their partners' path as being due to a lack of
mutual modelling accuracy instead of being due to spatial reasoning skills.

@@

\paragraph{Symmetry question} The correlation between \gModel{A}{B}  and
\gModel{B}{A}  is positive ($r = .41$) and significant ($p < .01$);  the more A
makes errors about B, the more B does the same.

@@

The independent variable was the presence of not of video link. The dependent
variable \gModel{A}{B} was subjectively by using 3 questionnaires: in the first
one, A described his or her own emotions \gmodel{A}{A} , while in the two other
questionnaire, A describes B's and C's emotions. The questionnaire included 18
items (7-point Likert Scale) describing emotions labeled as adjectives:
\emph{anxious}, \emph{enthusiastic}, \emph{agitated}, \emph{proud},
\emph{excited}, \emph{quiet}, \emph{calm}, \emph{stressed}, \emph{bored},
\emph{upset}, \emph{relaxed}, \emph{irritated}, \emph{determined},
\emph{hostile}, \emph{active}, etc. This list of emotions was
elaborated from \fixme{REF?}. The proposed emotions were \fixme{?}. \gmodel{A}{B} is a vector
of 18 numerical values ${x_1 \dots x_i}$ corresponding to their answers on each
questionnaire. \gModel{A}{B} has been computed as the correlation between the
two vectors (Eq.~\ref{eq:study3}).

@@

\begin{figure*}[ht!]
        \centering
        \includegraphics[width=0.9\textwidth]{image9.pdf}
        \caption{Average values of \Model{A}{B}{X} where X is one of the proposed
        emotions (max = 7).}
        \label{study3:deg_m_values}
\end{figure*}

@@

\paragraph{Grounding criterion} In this task, the grounding criterion was low,
but we did not evaluate task performance (\eg the quality of the jointly
produced concept map) but the learning gains. The correlation between
\gModel{A}{B} and A's learning gains is not significant ($\beta =.08, ,NS, N =
60$). It is also not significant within each condition.

\paragraph{Study-specific questions} We performed a non-parametric Mann-Whitney
test on post-test scores for electric questions and a one-way ANOVA on scores
for ionic questions (Levene tests for homogeneity of variances: $p = .02$ and
$ns$, respectively. Results  did not show any significant difference between the
\emph{same information} (SI) condition and the \emph{complementary information}
(CI) condition, neither for electric questions [$U = 388.50, z = -0.88, ns$] nor
for ionic questions [$F(1, 58) = 0.17, ns$].  The effect of scripts on
\gModel{A}{B} was not significant ($F(1, 58) = 0.78, ns$) when considering the
absolute difference between \gModel{A}{B} and B's post-test score. However, A
tended underestimate B's score in the SI condition ($M = -2.06$) and to
overestimate it in the CI condition ($M = 1.21$) ($F(1, 58) = 6.44, p<.01$).
Regarding to \gModel{A}{A}, there was no significant difference between
conditions.

@@

In this experiment, the symmetry of mutual modelling is only found when subjects
are in conditions of symmetry of information. This consolidates the hypothesis
of \gModel{A}{B} being a property of interactions in context rather than A's
cognitive attitude.

@@

This study investigates if \Model{A}{B}{knowledge} is related to learning
outcomes by comparing teams with or without a knowledge awareness tool (KAT),
\ie a tool that informs A about B's knowledge as measured through a pre-test.

@@

The KAT has a significant effect on \gModel{A}{B}: peers more accurately
estimated their partners knowledge ($M = 1.11$) than those in the control
condition [$M = .98, t(1, 60) = 3.19, p < .01$, Cohen's $d = 0.83$, large
effect]. This is a trivial result since the KAT provided them with an initial
\gmodel{A}{B}. However, subjects have to predict the post-test score while the
KAT informed them about the pre-test score. Actually, pairs in the KAT condition
produced significantly more instances of 3 specific categories of interactions:
(1) elaborated utterances with rich contents,  (2) utterances asking about the
other's knowledge such as ``Did you understand how transmission works?'' (3)
utterances describing one's own knowledge (\gmodel{A}{A}) such as ``I don't
remember the Ranvier's thing...''. These 3 categories provide different account
of \gModel{A}{B}: (1) as an effect of the quality of interaction, (2) as an
effect of A's effort to model B or (3) as B's effort to give cues to A about his
own knowledge.

@@

Out of 5 studies, 3 revealed a correlation between the model peers built about
each other: when A builds an accurate model of B, B also tends to build an
accurate model of A.  In one study, this was the case only in one condition.
The conclusion is hence that modelling is mutual but only in certain conditions,
summarized in Table~\ref{synthesis_table}.

@@

Coming back to our initial hypotheses, the $\Delta_2$ results in studies 1, 2
and 3 reinforce both $\mathcal{H}_{2}$ and $\mathcal{H}_{3}$. The
\emph{interaction hypothesis} $\mathcal{H}_{3}$ was that the activity of
modelling one's partner is not simply the result of an individual cognitive
effort but overall the side-effect of the quality of interactions. The
\emph{second-order-modelling hypothesis} $\mathcal{H}_{2}$ stated that, if A is
accurate in modelling B, A should notice when B misunderstands A and should be
able to repair. A good modeler would somehow drive the modelling of his or her
partner.  This \emph{drive} will however occur through verbal cues and repairs
and is hence not easy to differentiate from $\mathcal{H}_{3}$.  The
contradictory $\Delta_1$ results in studies 4 (to some extent) and 5 weaken the
hypothesis.

The triangular questions lead to similar contradictions. The $\Delta_2$
correlation between the \gmodel{A}{C} and \gmodel{B}{C} (studies 2 and 3?)
support $\mathcal{H}_{2}$ if modelling skills were purely individual, there would
be no reason for modelling skills of A and B to be correlated.  The role of C in
\gmodel{A}{C} and \gmodel{B}{C} probably explains this correlation.  Conversely,
the $\Delta_3$ correlation between the \gmodel{A}{B} and \gmodel{A}{C} (studies
3 and 2?) question $\mathcal{H}_{3}$: if the role of the modellee was so
important, it would lead be surprising to have by chance a correlation between
B's and C' ability to drive A's modelling.

In addition, the lack of correlation between \gmodel{A}{A} and \gmodel{A}{B}
($\Delta_2$ in study 4 and study 5) could also contributes to the idea that A's
modelling skills is not the key factor. However, between modelling someone and
modelling oneself, \ie  metacognition, they are so many differences, that we
would hardly conclude from that,

@@

Finally, let us stress the expressions we used, such as \gmodel{A}{B}, do not
imply we have a mechanical view of modelling. It's just a language for referring
to different components of modelling each other in teams.  This simple notation
emerges from the need to compare five mutual modelling studies; it did not
generate a consistent program of consistent studies.  Our results are not very
robust because they emerge from a \emph{post-hoc} reinterpretation of studies
that addressed different research questions (media richness, awareness tools,
scripts,...). This diversity makes our results difficult to integrate, partly
contradictory. Nonetheless, this diversity gives some generalizability: mutual
modelling has been investigated in different contexts (virtual space versus real
space), with different groups sizes (pairs and triads) and different tasks.
Moreover, these results have been found using different methods for measuring
modelling: on-task in study 1 versus off-task in study 2, subjective validation
in study 1 versus objective validation in study 2 (comparing A's model with B's
behavior).

>>>>

Initial common grounds are also initiated by co-presence: they include events to
which $A$ and $B$ attended together~\citep{clark2002definite} in the physical space
or in our cultural space (\eg ‘09-11'). Co-presence means that we can refer to
a shared objects and event,-s it does of course not imply that we give them the
same meaning. Namely, a shared screen does not mean a shared
understanding~\citep{dillenbourg2006sharing}.

@@

Mutual modelling does not occur in a vacuum but it is highly contextualized. REF
reviews the features of the collaborative situation, namely the media
(cotemporality… ), may facilitate or hamper mutual modelling. Hutchins (SILENCE)
reported a study in which a short silence between two pilots was perfectly
interpreted because it occurred in a highly constrained communication context.
Some environments are more productive than others in helping peers to detect
their misunderstandings. Roschelle~\citep{roschelle1995construction} reformulate
the design of CSCL interfaces as providing ways for peer to detect and repairs
their misunderstanding. In CSCW, researchers have explored various so-called
``awareness tools'', \ie functionalities that inform $A$ is about $B$'s actions that A
could not directly perceived because $B$ was working on a different subset of the
virtual space. Different awareness tools will be addressed in this contribution
since they allowed us to manipulate experimentally the mutual modelling activity.

@@

To report experiments on mutual modelling, we suggest
the notation \model{A}{B}{X} to denote ``A knows that $B$ knows X''. This is a
simple but useful reduction to reason on mutual modelling. This
notation does not mean $A$ has an explicit, monolithic representation of B: it
must be understood as an abstraction referring to complex socio-cognitive
processes. Besides, we refer to the \emph{degree of accuracy} of the model as
\Model{A}{B}{X}.

@@

Based on these 3 parameters, the probability of making an action $\alpha_{t_1}$ about
content $X$ at time $t_1$ during task T in order to increase \Model{A}{B}{X}
at time $t_2$ is the ratio between how much it is needed  ((2)-(1)) and how much it
costs (3)~\citep{traum1996miscommunication}:

@@

    \begin{enumerate}
        \item \model{A}{B}{emotion}: how accurately $A$ perceives $B$'s emotional state
            (study 3);

        \item \model{A}{B}{actions} is about how well $A$ guesses what action $B$ has
            done (study 2) or will do next  (study 1)

        \item \model{A}{B}{knowledge}: how accurately $A$ estimates $B$'s knowledge
            with respect to the material they learn together (study 4 and 5)

@@

    \item $cost(\alpha)$ In all studies but study 4, the cost of  grounding is
        an independent variable. Study 3 uses media richness as independent
        variable, with the hypothesis that modelling emotions is ``cheaper'' with a
        richer medium, \ie  when peers can see each other.  Studies 1,2 and 4
        use awareness tools which, in principle, reduce the cost of mutual modelling, but do
        not eliminate all costs: if the tool provide $A$ with information about
        what $B$ does/knows, this additional information may actually increase
        cognitive load. Awareness tools constitute as a kind of mutual modelling prosthesis,
        and, like any prosthesis, they many augment mutual modelling (by facilitating it or
        even scaffolding it) or inhibit it (by making it useless).

@@

\begin{itemize}
    \item {\bf Capturing \model{A}{B}{X}}: The simplest method is to ask $A$ what (s)he
        believes about what $B$ knows, feels, intends to do, etc. This raises
        obvious methodological concerns since such a question triggers a
        modelling process beyond what would naturally occur. To avoid this
        bias, one can estimate mutual modelling after task completion. Then, the
        obvious drawback are memory losses and by post-hoc reconstruction.  The
        first method was used in study 2 and the second one in the other
        studies. Another option would be to rely on external behavioural metrics
        like eye-tracking: we hypothesise for instance that the fixation time
        reflects the efforts engaged by the human to understand, hence, model,
        the others. Such an approach has however not yet been investigated in
        the presented studies.

@@

\begin{itemize}
    \item $\mathcal{H}_{1}$: $\mathcal{M}^{\circ}(A,B)$ depends upon $A$'s ability or effort
        to model $B$,

    \item $\mathcal{H}_{2}$: $\mathcal{M}^{\circ}(A,B)$ depends upon  $B$'s ability of
        effort to help $A$ to model him/herself

    \item $\mathcal{H}_{3}$: $\mathcal{M}^{\circ}(A,B)$ depends upon the quality of
        interactions among $A$ and B

@@

$\mathcal{H}_{2}$ is also called a second level modelling hypothesis since H
needs to monitor $B$ to see if $A$ understood him/her
$\mathcal{M}(B,(A,\mathcal{M}(A,B)))$

@@

This leads to two \emph{triangle questions} (Fig.~\ref{mm_triangles}): Do $A$ and
B have the same accuracy when modelling C? $\Delta_2 = \Delta(\M{A}{C}{X},
\M{B}{C}{X})$. If it is the same, $\mathcal{H}_{2}$ and $\mathcal{H}_{3}$ gain
over $\mathcal{H}_{1}$

Conversely, does $C$ model more accurately $A$ than B? $\Delta_3= \Delta(\M{C}{A}{X},
\M{C}{B}{X})$ A positive answer would support $\mathcal{H}_{3}$.

@@

The independent variable was the availability of an awareness tool that shows to
player $A$  the location and gaze direction of player $B$. In the awareness
condition, players could switch to the \emph{scout mode} where they could view what
their partner was looking at. We hypothesize that this would enable subjects to
more accurately infer their teammate's intentions. Each player sat in front of a
distinct computer located in different rooms.

@@

In order to evaluate \gModel{A}{B} during the task, we used two questionnaires
(Fig.~\ref{study1:questionnaires}) that were displayed during each of the three
games, as a transparent layer appearing over the game display. The first
questionnaire concerned the player's intended actions. The second questionnaire
asked each player about what he thought her or his partner was intending to do.
Some answers were identical in both questionnaires (like ``adjusting a shot'')
while others were reversed (``to guide my partner'' versus ``to guide me''). We
chose this subjective measure of accuracy ($\Delta(\M{A}{B}{x}, \M{B}{B}{x})$)
rather than an objective measure (\ie the model \gmodel{A}{B} is compared to $B$'s
next action) because some the activities proposed by the questionnaire were not
observable by the environment (\eg establishing a strategy). We counted
\Model{A}{B}{activity_{game_{i}}}) as the number of common answers between
questionnaires \gmodel{A}{B} and \gmodel{B}{B} in each game and computed the
average value a across the 3 games.

@@

This study concerns a collaborative game that occurred in the physical
space~\citep{nova2006underwhelming}. We studied whether players build an accurate
model of the path followed by their partners because this path reflected their
problem solving strategy. We used an objective measure of \gModel{A}{B}: the
distance between where $A$ believes $B$ has been walking and where $B$ actually went.
The main hypothesis concerned the effect of awareness tools on group performance
and on \gModel{A}{B}.

@@

{\sc CatchBob} is a mobile game in which groups of 3 players have to solve a
joint task. The game was played on EPFL campus. Participants had to find a
virtual object (\emph{Bob}) and ``to catch it'' by forming a triangle around it.
Players used a Tablet PC that displayed a map of the campus and an indication of
their personal distance to Bob. Their annotations on the map were shared with
the two other players ($A$ could see what $B$ and $C$ wrote). These annotations faded
out after a few minutes to avoid covering the full display. The awareness tool
displayed as well the location of the two other players on the map. The
availability of location awareness tool constituted our independent variable.

\begin{figure*}[h!t]
        \centering
        \begin{subfigure}{.3\textwidth}
            \includegraphics[width=\linewidth]{image6.png}
            \caption{A's drawing of $B$'s path.}
        \end{subfigure}
        \begin{subfigure}{.3\textwidth}
            \includegraphics[width=\linewidth]{image7.png}
            \caption{Actual path followed by $B$.}
        \end{subfigure}
        \caption{Reported and actual path of one of the player, during the {\sc
        CatchBob} game.}
        \label{study2:paths}
\end{figure*}

@@

The independent variable was the awareness tool: the control condition (without
tool) and two experimental conditions: synchronous awareness (display current
position of each player) and asynchronous awareness (display current position of
each player and their recent spatial trace).  As a dependent variable, we had
the task performance which was the distance covered by the team to catch Bob and
\gModel{A}{B}. To estimate \gModel{A}{B}, we asked players to draw on paper
their own path and the path of each of their partners after the game. This
enabled us to calculate the number of errors players made while drawing the path
of their partners. We compared the path that player $A$ attributed to $B$ with $B$'s
real path recorded by the system and the same for $A$ \& $C$ and $B$ \& $C$ as depicted
on Fig.~\ref{study2:paths}.

\gModel{A}{B} is the sum of errors made by $A$ about $B$'s paths. An error was
either drawing a place where the partner had not been or not drawing a place
where he/she had gone. One could argue that \gModel{A}{B} is biased by the
subjects' ability to translate their trajectories souvenir into a map drawing.
However, 85\% of subjects made no mistake at all when drawing their own path. We
therefore consider mistakes in their partners' path as being due to a lack of
mutual modelling accuracy instead of being due to spatial reasoning skills.

@@

\paragraph{Symmetry question} The correlation between \gModel{A}{B}  and
\gModel{B}{A}  is positive ($r = .41$) and significant ($p < .01$);  the more A
makes errors about $B$, the more $B$ does the same.

@@

The independent variable was the presence of not of video link. The dependent
variable \gModel{A}{B} was subjectively by using 3 questionnaires: in the first
one, $A$ described his or her own emotions \gmodel{A}{A} , while in the two other
questionnaire, $A$ describes $B$'s and C's emotions. The questionnaire included 18
items (7-point Likert Scale) describing emotions labeled as adjectives:
\emph{anxious}, \emph{enthusiastic}, \emph{agitated}, \emph{proud},
\emph{excited}, \emph{quiet}, \emph{calm}, \emph{stressed}, \emph{bored},
\emph{upset}, \emph{relaxed}, \emph{irritated}, \emph{determined},
\emph{hostile}, \emph{active}, etc. This list of emotions was
elaborated from \fixme{REF?}. The proposed emotions were \fixme{?}. \gmodel{A}{B} is a vector
of 18 numerical values ${x_1 \dots x_i}$ corresponding to their answers on each
questionnaire. \gModel{A}{B} has been computed as the correlation between the
two vectors (Eq.~\ref{eq:study3}).

@@

\begin{figure*}[ht!]
        \centering
        \includegraphics[width=0.9\textwidth]{image9.pdf}
        \caption{Average values of \Model{A}{B}{X} where $X$ is one of the proposed
        emotions (max = 7).}
        \label{study3:deg_m_values}
\end{figure*}

@@

\paragraph{Grounding criterion} In this task, the grounding criterion was low,
but we did not evaluate task performance (\eg the quality of the jointly
produced concept map) but the learning gains. The correlation between
\gModel{A}{B} and $A$'s learning gains is not significant ($\beta =.08, ,NS, N =
60$). It is also not significant within each condition.

\paragraph{Study-specific questions} We performed a non-parametric Mann-Whitney
test on post-test scores for electric questions and a one-way ANOVA on scores
for ionic questions (Levene tests for homogeneity of variances: $p = .02$ and
$ns$, respectively. Results  did not show any significant difference between the
\emph{same information} (SI) condition and the \emph{complementary information}
(CI) condition, neither for electric questions [$U = 388.50, z = -0.88, ns$] nor
for ionic questions [$F(1, 58) = 0.17, ns$].  The effect of scripts on
\gModel{A}{B} was not significant ($F(1, 58) = 0.78, ns$) when considering the
absolute difference between \gModel{A}{B} and $B$'s post-test score. However, A
tended underestimate $B$'s score in the SI condition ($M = -2.06$) and to
overestimate it in the CI condition ($M = 1.21$) ($F(1, 58) = 6.44, p<.01$).
Regarding to \gModel{A}{A}, there was no significant difference between
conditions.

@@

In this experiment, the symmetry of mutual modelling is only found when subjects
are in conditions of symmetry of information. This consolidates the hypothesis
of \gModel{A}{B} being a property of interactions in context rather than $A$'s
cognitive attitude.

@@

This study investigates if \Model{A}{B}{knowledge} is related to learning
outcomes by comparing teams with or without a knowledge awareness tool (KAT),
\ie a tool that informs $A$ about $B$'s knowledge as measured through a pre-test.

@@

The KAT has a significant effect on \gModel{A}{B}: peers more accurately
estimated their partners knowledge ($M = 1.11$) than those in the control
condition [$M = .98, t(1, 60) = 3.19, p < .01$, Cohen's $d = 0.83$, large
effect]. This is a trivial result since the KAT provided them with an initial
\gmodel{A}{B}. However, subjects have to predict the post-test score while the
KAT informed them about the pre-test score. Actually, pairs in the KAT condition
produced significantly more instances of 3 specific categories of interactions:
(1) elaborated utterances with rich contents,  (2) utterances asking about the
other's knowledge such as ``Did you understand how transmission works?'' (3)
utterances describing one's own knowledge (\gmodel{A}{A}) such as ``I don't
remember the Ranvier's thing...''. These 3 categories provide different account
of \gModel{A}{B}: (1) as an effect of the quality of interaction, (2) as an
effect of $A$'s effort to model $B$ or (3) as $B$'s effort to give cues to $A$ about his
own knowledge.

@@

Out of 5 studies, 3 revealed a correlation between the model peers built about
each other: when $A$ builds an accurate model of $B$, $B$ also tends to build an
accurate model of A.  In one study, this was the case only in one condition.
The conclusion is hence that modelling is mutual but only in certain conditions,
summarized in Table~\ref{synthesis_table}.

@@

Coming back to our initial hypotheses, the $\Delta_2$ results in studies 1, 2
and 3 reinforce both $\mathcal{H}_{2}$ and $\mathcal{H}_{3}$. The
\emph{interaction hypothesis} $\mathcal{H}_{3}$ was that the activity of
modelling one's partner is not simply the result of an individual cognitive
effort but overall the side-effect of the quality of interactions. The
\emph{second-order-modelling hypothesis} $\mathcal{H}_{2}$ stated that, if $A$ is
accurate in modelling $B$, $A$ should notice when $B$ misunderstands $A$ and should be
able to repair. A good modeler would somehow drive the modelling of his or her
partner.  This \emph{drive} will however occur through verbal cues and repairs
and is hence not easy to differentiate from $\mathcal{H}_{3}$.  The
contradictory $\Delta_1$ results in studies 4 (to some extent) and 5 weaken the
hypothesis.

The triangular questions lead to similar contradictions. The $\Delta_2$
correlation between the \gmodel{A}{C} and \gmodel{B}{C} (studies 2 and 3?)
support $\mathcal{H}_{2}$ if modelling skills were purely individual, there would
be no reason for modelling skills of $A$ and $B$ to be correlated.  The role of $C$ in
\gmodel{A}{C} and \gmodel{B}{C} probably explains this correlation.  Conversely,
the $\Delta_3$ correlation between the \gmodel{A}{B} and \gmodel{A}{C} (studies
3 and 2?) question $\mathcal{H}_{3}$: if the role of the modellee was so
important, it would lead be surprising to have by chance a correlation between
B's and C' ability to drive $A$'s modelling.

In addition, the lack of correlation between \gmodel{A}{A} and \gmodel{A}{B}
($\Delta_2$ in study 4 and study 5) could also contributes to the idea that $A$'s
modelling skills is not the key factor. However, between modelling someone and
modelling oneself, \ie  metacognition, they are so many differences, that we
would hardly conclude from that,

@@

Finally, let us stress the expressions we used, such as \gmodel{A}{B}, do not
imply we have a mechanical view of modelling. It's just a language for referring
to different components of modelling each other in teams.  This simple notation
emerges from the need to compare five mutual modelling studies; it did not
generate a consistent program of consistent studies.  Our results are not very
robust because they emerge from a \emph{post-hoc} reinterpretation of studies
that addressed different research questions (media richness, awareness tools,
scripts,...). This diversity makes our results difficult to integrate, partly
contradictory. Nonetheless, this diversity gives some generalizability: mutual
modelling has been investigated in different contexts (virtual space versus real
space), with different groups sizes (pairs and triads) and different tasks.
Moreover, these results have been found using different methods for measuring
modelling: on-task in study 1 versus off-task in study 2, subjective validation
in study 1 versus objective validation in study 2 (comparing $A$'s model with $B$'s
behavior).
